AUTOMATED TRANSCRIPTION OF DRUMSOUNDS

### 2017-08-17 Latex/Paper/main.tex
Countercheck

As mentioned above he precision of the detected peak time point is is only precise within a range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
The precision could be improved by using a sinc interpolation to exactly determine the point of inflection.

@@

In closing we have presented an algorithm in this paper that gives satisfying results when trying to extract the exact time points at which base drum hits happen in a drum track.
It can easily be extended to other percussive instruments and maybe even other melodic instruments.
The accuracy and precision could be improved in future work by the methods mentioned.

>>>>

As mentioned above he precision of the detected peak time point is only precise within a range of approx. 12 ms since only the STFT frame it occurring in can be tracked.
The precision could be improved by using a sinc interpolation to exactly determine the point of inflection.

@@

In closing we have presented an algorithm in this paper that gives satisfying results when trying to exact the exact time points at which base drum hits happen in a drum track.
It can easily be extended to other percussive instruments and maybe even other melodic instruments.
The accuracy and precision could be improved in future work by the methods mentioned.
